---
title: " Novoalign Testing Report"
author: "Muhamad Amir Hafizin"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
output:
   slidy_presentation:
html_document:
theme: united
---

# BASIC COMMAND
* Reference Gene: Arabidopsis thaliana.TAIR10
	+ 119,146,348 bp
	+ 121.7 MB -> 2.6 GB

* Build using the ART
* Using time -verbose
* Cite 
	+ Hatem A., Bozdag D., Toland A.E., Catalyurek U.V.Benchmarking short sequence mapping tools. BMC Bioinform. 2013;14:184.
	+ Thole J.M., Beisner E.R., Liu J., Venkova S.V., Strader L.C. Abscisic acid regulates root elongation through the activities of auxin and ethylene in Arabidopsis thaliana. G3 (Bethesda) 2014;4:1259–1274. doi: 10.1534/g3.114.011080

## ART
* The coding for Building is: 
	+ art_illumina -ss HS20 -sam -i refseq  -l 100 -f 10 -o ilumina
		+ "-ss"  = The name of Illumina sequencing system of the built-in profile used for simulation
		+ "HS20" = sequencing system ID names for HiSeq 2000 (100bp)
		+ "sam"  = indicate to generate SAM alignment file
		+ "i"    = the filename of input DNA/RNA reference
		+ "l"    = the length of reads to be simulated
		+ "f"    = the fold of read coverage to be simulated or number of reads/read pairs generated for each amplicon
		+ "o"    = the prefix of output filename

*****

## NOVOINDEX
* The coding use
	+ novoindex thaliana.idx Arabidopsis thaliana.TAIR10.fa
		+ k = 11
		+ s = 1

## NOVOALIGN
* The coding use 
	+ novoalign -c 5 -t 10 -f ilumina.fq -d thaliana.idx -o SAM 2> novoalign.stderr > parameter.sam
		+ "c" =  Sets  number of threads to use.
		+ "t" =  Sets the maximum alignment score acceptable for the best alignment. 
		+ "d" =  Full pathname of indexed reference sequence created by novoindex
		+ "o" =  Specifies the report name and format


*****

# Table
```{r, echo= FALSE, results="asis"}
tab= read.csv("/export/home/amirh/novoalign_testing/test/average.csv",header=TRUE)
library("knitr")
kable(tab)
```
*****

# Graph
```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/average1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,1],main="Time(Multithreading/c=5) VS Threshold(-t)",ylab="Time(min)",xlab="Threshold(-t)",border="red",ylim=c(0,12))
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/try.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,1],main="Time(c=1/CPU=82%) VS Threshold(-t)",ylab="Time(min)",xlab="Threshold(-t)",border="red",ylim=c(0,100))
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/average1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,4],main="CPU percent(-c5) VS Threshold(-t)",ylab="CPU percent(%)",xlab="Threshold(-t)",border="red",ylim=c(400,500))
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/average1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,8],main="Unique Alignment VS Threshold(-t)",ylab="No of Alignment",xlab="Threshold(-t)",border="red")
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/average1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,10],main="Multi Mapped VS Threshold(-t)",ylab="No of Alignment",xlab="Threshold(-t)",border="red")
```
*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/average1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,12],main="No mapping VS Threshold(-t)",ylab="No Of Alignment",xlab="Threshold(-t)",border="red")
```

# Table
```{r, echo= FALSE, results="asis"}
tab= read.csv("/export/home/amirh/novoalign_testing/test/align.csv",header=TRUE)
library("knitr")
kable(tab)
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/align1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,1],main="mapped region VS Threshold(-t)",ylab="No of Alignment(%)",xlab="Threshold(-t)",border="red")
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/align1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,2],main="Unmapped region VS Threshold(-t)",ylab="MultiMapped(%)",xlab="Threshold(-t)",border="red")
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/align1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,3],main="mapping inside region VS Threshold(-t)",ylab="No of Alignment(%)",xlab="Threshold(-t)",border="red")
```

*****

```{r, echo= FALSE, results="asis"}
x<-read.csv("/export/home/amirh/novoalign_testing/test/align1.csv",sep=",",header=TRUE,stringsAsFactors = TRUE)
d<-t(x)
barplot(d[,4],main="mapping outside region VS Threshold(-t)",ylab="No of Alignment(%)",xlab="Threshold(-t)",border="red")
```

*****

# Total Read sequence = 11947007

