---
title: " Weekly Report"
author: "Muhamad Amir Hafizin"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
runtime: shiny
output:
   html_document:
toc: true
theme: united
---

<!-- above is to decleared the output of file-->
<!-- # is the header-->

# Learning point
<!-- *with space is to decleared as bullet-->
* Introduction to bash
* Introduction to R
* Introduction to Markdown and RMarkdown
* Conversion of RMarkdown to HTML and PDF format 
* Introduction of Shiny R
* Introduction of pandoc
* Introduction of Rmarkdown
* Basic of scripting in terminal

# Objective
<!-- ** ** is for the bold while * * is for the italic-->
Convert our in-house wikia to **Rmarkdown** format and *PDF format*. Upload each of these documents to a GIT repository for access by all Novocraft team members. 

# Expected Outcome:

* A git repository with the in-house wikia  stored in the same folder structure
* All wikia pages to be converted to RMarkdown
* RMarkdown to be converted to PDF
* Rscript to convert wikia pages to RMarkdown and upload to GIT HUB
* Rmarkdown file that contain the the daily schedule,shiny in the PDF,HTML and Slides
*

DURATION: ***2 Weeks***

<!---for the table of daily schedule-->
<!---i using kable to produce table that work with html and pdf format-->
# Daily Report
```{r, echo= FALSE, results="asis"}
tab= read.csv("dailyreport1.csv",header=TRUE)
knitr::kable(tab)
```

*****

<!---for the table selected of daily schedule using shiny-->
```{r,echo = FALSE, include=TRUE}
library(shiny)
report <-read.csv("dailyreport1.csv",header=TRUE)
shinyApp(
ui <- fluidPage(
selectInput("Date","Choose Date",
c(unique(as.character(report$Date)))),
dataTableOutput("result")
),

server = function(input,output){
output$result <- renderDataTable({
report <- read.csv("dailyreport1.csv",header=TRUE)
report <- report[report$Date == input$Date,]
})
},
)

```

*****

<!--[]() is how to link the website to the citation-->
## The link to [Novocraft wikia](http://dev.novocraft.com/trac/trac_backup/wiki) house and [Novocraft website](http://www.novocraft.com/)

